Reproducible_Research_Project01
================================

#### <br />Setting global option
```{r setup, include =TRUE}
knitr::opts_chunk$set(echo = T)
```

#### Load the input data
```{r}
setwd("~/Desktop/Coursera/Reproducible Research/Project01")
activity <- read.csv("activity.csv")
```

### <br />**What is mean total number of steps taken per day?**
#### Calculate the total number of steps taken per day
```{r}
steps.all <- aggregate(steps~date, activity, sum, na.rm=TRUE)
head(steps.all)
```

#### Make a histogram of the total number of steps taken each day
```{r}
hist(steps.all$steps, breaks = 10, xlab='Total number of steps taken each day')
```

#### Calculate and report the mean and median of the total number of steps taken per day
```{r}
mean(steps.all$steps, na.rm = TRUE)
median(steps.all$steps, na.rm = TRUE)
```
* The mean of daily is`r mean(steps.all$steps)` steps.
* The median of daily is `r median(steps.all$steps)` steps.

#### <br />
### **What is the average daily activity pattern?**
#### Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
steps.interval<-aggregate(steps~interval, data=activity, mean,na.rm=TRUE)
plot(steps~interval,data=steps.interval,type="l")
```

#### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps? 
```{r}
MaxInt5min <- steps.interval[which.max(steps.interval$steps),]$interval
```
* On average across all the days in the dataset, the 5-min interval that contains the maximum number of steps is `r MaxInt5min`

### <br />**Imputing Missing Values**
#### Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
sum(is.na(activity$steps))
```
* The total missing number of rows: `r sum(is.na(activity$steps))`

#### Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.
```{r}
activity$imputedSteps <- ifelse(!is.na(activity$steps), activity$steps, round(steps.interval$steps[match(activity$interval, steps.interval$interval)],0))
```

#### Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r}
activeImputed <- activity[-c(1)]
activeImputed <- activeImputed[, c(3,1,2)]
names(activeImputed)[1] <- paste("steps")
```

#### Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. 
```{r}
steps.all.activeImputed <-aggregate(steps~date, activeImputed ,sum)
hist(steps.all.activeImputed$steps, breaks = 10, xlab='Steps' )
mean(steps.all.activeImputed$steps)
median(steps.all.activeImputed$steps)
```
* The NEW mean of daily steps is `r mean(steps.all.activeImputed$steps)` steps.
* the NEW median of daily steps is `r median(steps.all.activeImputed$steps)` steps.

### <br />**Are there differences in activity patterns between weekdays and weekends?**
#### Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r}
activeImputed$date <- as.Date(activeImputed$date, format="%Y-%m-%d")
activeImputed$weekday <- weekdays(activeImputed$date)
activeImputed$DayType <- ifelse(activeImputed$weekday=='Saturday' | activeImputed$weekday=='Sunday', 'weekend','weekday')
```

#### Make a panel plot containing a time series plot (i.e. \color{red}{\verb|type = "l"|}type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).
```{r}
library(ggplot2)
steps.int.Daytype.activeImputed <- aggregate(steps~interval+DayType, activeImputed ,mean)
ggplot(steps.int.Daytype.activeImputed, aes(interval, steps)) + 
    geom_line() + 
    facet_grid(DayType ~ .) +
    xlab("5-minute interval") + 
    ylab("avarage number of steps")
```